Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-17 paper/paper.tex
Fix blatant lies

Some filtering techniques exploit invariant properties, i.e.\ properties associated with nodes such
that nodes may be matched only if they have compatible properties. A classical property is the
degree: a pattern node $u\in N_p$ may be matched with a target node $v\in N_t$ only if
$d^\circ(u)\leq d^\circ(v)$. This property is usually used at the beginning of the search to reduce
the set of candidate pairs to $\{(u,v)\in N_p\times N_t\;|\;d^\circ(u)\leq d^\circ(v)\}$.  Other
examples of invariant properties are the number of cycles of length $k$ passing through the node,
and the number of cliques of size $k$ containing the node, which must be smaller for a pattern node
than for its matched target node.  Invariant properties may also be associated with pairs of nodes.
For example, the number of paths of length $k$ between two pattern nodes is smaller than or equal to
the number of paths of length $k$ between the target nodes with which they may be matched.

These invariant properties are used, for example,
\begin{itemize}
\item by Battiti and Mascia~\cite{battiti-mascia07}, to remove candidate pairs $(u,v)\in N_p\times
    N_t$ such that the number of paths starting from  pattern node $u$ is greater than the number of
    paths starting from  target node $v$;
\item by Audemard et al.~\cite{Audemard:2014} to generalise the locally all-different constraint
    proposed by Solnon~\cite{Solnon:2010} so that it ensures that a subset of pattern nodes can be
    matched with all different compatible target nodes, where compatibility is defined with respect
    to invariant properties;
\item by McCreesh and Prosser~\cite{McCreesh:2015} to filter the set of candidate couples before
    starting the search, and to generate additional implied adjacency-like constraints which are
    processed during search.
\end{itemize}

@@

\GlasgowTwo becomes the best solver for time limits larger than \SI{3000}{\ms}.
As we
increase the CPU time limit, variants of \Glasgow with longer paths (\GlasgowThree and \GlasgowFour)
become better. This is what we expect, as more reasoning is expensive, but
increases the potential
reduction of the search space. In particular, the relative performance of \Glasgow variants is
monotone in the time it takes to solve the instance---\GlasgowOne is best at first, but gets worse as
the time to solve the instance increases until \GlasgowTwo is better. After that point, \GlasgowOne is
never better than \GlasgowTwo again. The same is true for path lengths 3 and 4.

The figure illustrates the potential for portfolios and algorithm selection we have. There is
clearly no single solver that dominates throughout.

>>>>

Some filtering techniques exploit invariant properties, i.e.\ properties associated with nodes such
that nodes may be matched only if they have compatible properties. A classical property is the
degree: a pattern node $u\in N_p$ may be matched with a target node $v\in N_t$ only if
$d^\circ(u)\leq d^\circ(v)$. This property is usually used at the beginning of the search to reduce
the set of candidate pairs to $\{(u,v)\in N_p\times N_t\;|\;d^\circ(u)\leq d^\circ(v)\}$.  Other
examples of invariant properties are the number of cycles of length $k$ passing through the node,
and the number of cliques of size $k$ containing the node, which must be smaller for a pattern node
than for its matched target node.  Invariant properties may also be associated with pairs of nodes.
For example, the number of paths of length $k$ between two pattern nodes is smaller than or equal to
the number of paths of length $k$ between the target nodes with which they may be matched.
These invariant properties are used, for example,

\begin{itemize}[nosep]
\item by Battiti and Mascia~\cite{battiti-mascia07}, to remove candidate pairs $(u,v)\in N_p\times
    N_t$ such that the number of paths starting from  pattern node $u$ is greater than the number of
    paths starting from  target node $v$;
\item by Audemard et al.~\cite{Audemard:2014} to generalise the locally all-different constraint
    proposed by Solnon~\cite{Solnon:2010} so that it ensures that a subset of pattern nodes can be
    matched with all different compatible target nodes, where compatibility is defined with respect
    to invariant properties;
\item by McCreesh and Prosser~\cite{McCreesh:2015} to filter the set of candidate couples before
    starting the search, and to generate additional implied adjacency-like constraints which are
    processed during search.
\end{itemize}

@@

\GlasgowTwo becomes the best solver for time limits larger than \SI{3000}{\ms}.
As we increase the CPU time limit, the performance of variants of \Glasgow with
longer paths (\GlasgowThree and \GlasgowFour) improves. This is what we expect,
as more reasoning is expensive, but increases the potential reduction of the
search space. Eventually, \GlasgowTwo and \GlasgowThree become very closely
matched, and with runtimes very close to the limit, \GlasgowFour nearly catches
up. (This behaviour is class-dependent: over class 2, for example, the behavior
is roughly monotone, with \GlasgowOne dominating for low runtimes, then
\GlasgowTwo, then \GlasgowThree, then \GlasgowFour each becoming best as the runtimes
increase.)

The figure illustrates the potential for portfolios and algorithm selection we have: there is
clearly no single solver that dominates throughout.
